Manuscript1_figures

### 2025-05-07 Manuscript1_figures.Rmd
Removing relative file path and adding missing pacakge to p_load

## Figure 8. Cumulative Sed Mass Plot
```{r Figure 8 script, eval=TRUE, include=FALSE}
plot_vline <- read_csv('~/Documents/R Projects/Sed Traps/TO_Dates.csv') %>% 
  mutate(Date = as.Date(Date),
         Event = as.factor(Event),
         Reservoir = as.factor(Reservoir),
         Layer = 'Hypolimnion')

>>>>

## Figure 8. Cumulative Sed Mass Plot
```{r Figure 8 script, eval=TRUE, include=FALSE}
plot_vline <- read_csv('TO_Dates.csv') %>% 
  mutate(Date = as.Date(Date),
         Event = as.factor(Event),
         Reservoir = as.factor(Reservoir),
         Layer = 'Hypolimnion')
